---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/",
  out.width = "100%"
)
```



# Root-Research-Project-Compendium


<!-- badges: start -->
[![R CMD Check](https://github.com/brainworkup/pj.research.compendium.root/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/brainworkup/pj.research.compendium.root/actions/workflows/R-CMD-check.yaml)
[![License: MIT](https://img.shields.io/badge/License-MIT-yellow.svg)](https://choosealicense.com/licenses/mit/)
[![LifeCycle](https://img.shields.io/badge/lifecycle-experimental-orange)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![Project Status: Active](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![Dependencies](https://img.shields.io/badge/dependencies-18/127-red?style=flat)](#)
<!-- badges: end -->


Research Compendium of the project **{{ TODO: }}**



### How to cite

Please cite this compendium as: 

> **{{ PLEASE ADD A CITATION }}**



### Content

This repository is structured as follow:

- [`data/`](https://github.com/brainworkup/pj.research.compendium.root/tree/master/data):
contains all raw data required to perform analyses

- [`analysis/`](https://github.com/brainworkup/pj.research.compendium.root/tree/master/analysis/):
contains R scripts to run each step of the workflow

- [`code/`](https://github.com/brainworkup/pj.research.compendium.root/tree/master/code/):
contains R scripts to run each step of the workflow

- [`outputs/`](https://github.com/brainworkup/pj.research.compendium.root/tree/master/outputs):
contains all the results created during the workflow

- [`figures/`](https://github.com/brainworkup/pj.research.compendium.root/tree/master/figures):
contains all the figures created during the workflow

- [`R/`](https://github.com/brainworkup/pj.research.compendium.root/tree/master/R):
contains R functions developed especially for this project

- [`man/`](https://github.com/brainworkup/pj.research.compendium.root/tree/master/man):
contains help files of R functions

- [`DESCRIPTION`](https://github.com/brainworkup/pj.research.compendium.root/tree/master/DESCRIPTION):
contains project metadata (author, date, dependencies, etc.)

- [`make.R`](https://github.com/brainworkup/pj.research.compendium.root/tree/master/make.R):
main R script to run the entire project by calling each R script stored in the `analyses/` folder



### Usage

- Clone this repository
- Open a terminal
- Build the Docker image with:

```sh
docker build -t "pj.research.compendium.root" .
```

- Start a container based on this image:

```sh
docker run --rm -p 127.0.0.1:8787:8787 -e DISABLE_AUTH=true pj.research.compendium.root
```

- On a web browser enter this URL: `127.0.0.1:8787`. A new RStudio Server
instance will be available.
- To run the analysis:

```{r eval = FALSE}
source("make.R")
```



### Notes

- All required packages, listed in the `DESCRIPTION` file, will be installed (if necessary)
- All required packages and R functions will be loaded
- Some analyses listed in the `make.R` might take time
